\myTitle

### 2024-03-25 body-text-of-paper.tex
added the supplement

SNP filtering resulted in 14,233 loci that were used for subsequent analysis.
Using the 160 empirical samples, ADMIXTURE results supported the identification of
$K=3$ genetic clusters that grouped individuals from each of the core populations into 3 clusters
while the 40 individuals from the contact regions were highly admixed. The
$F_\mathrm{ST}$ divergence from ADMIXTURE was:
$F_\mathrm{ST} = 0.24$ for Pop1-Pop2,
$F_\mathrm{ST} = 0.14$ for Pop1-Pop3 and
$F_\mathrm{ST} = 0.13$ for Pop2-Pop3.

>>>>

SNP filtering resulted in 14,233 loci that were used for subsequent analysis.
Using the 160 empirical samples, ADMIXTURE results supported the identification of
$K=3$ genetic clusters (Figure S1) that grouped individuals from each of the core populations into 3 clusters
while the 40 individuals from the contact regions were highly admixed (Figure S2). The
$F_\mathrm{ST}$ divergence from ADMIXTURE was:
$F_\mathrm{ST} = 0.24$ for Pop1-Pop2,
$F_\mathrm{ST} = 0.14$ for Pop1-Pop3 and
$F_\mathrm{ST} = 0.13$ for Pop2-Pop3.
